---
output:
  md_document:
    variant: gfm
---

[![Travis build status](https://travis-ci.org/aedobbyn/multicolor.svg?branch=master)](https://travis-ci.org/aedobbyn/multicolor)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# multicolor `r emo::ji("art")`

Apply multiple colors to your messages and warnings. Built on the [`crayon`](https://github.com/r-lib/crayon) package. Pairs nicely with [`cowsay`](https://github.com/sckott/cowsay).

### Installation 

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("aedobbyn/multicolor")
```


## Usage

```{r}
library(multicolor)
```

Supply a character vector of colors to `colors`. Defaults to rainbow, i.e., `c("red", "orange", "yellow", "green", "blue", "purple")`. The text supplied will be divided into even(ish) vertical chunks of those colors.

```{r example}
multi_color("Hello world")
```

If you want the bare string back with color encodings, use `type = "string"`.

```{r}
multi_color("Some words here",
  type = "string")
```

The default is to message the result. 

```{r}
multi_color("Some words here",
            sample(colors(), 
                   sample(10, 1)))
```


Pairs nicely with the [`cowsay`](https://github.com/sckott/cowsay) package:

```{r}
library(cowsay)

say(what = "holygrail", 
    by = "yoda",
    what_color = "olivedrab",
    by_color = c("tomato1", "saddlebrown", "springgreen4", "turquoise2"))
```

Error in style:

```{r}
my_msg <- 
  say(what = "Error: something went horribly wrong",
    by = "rms",
    what_color = "orange",
    by_color = c("red", "red", "orange", "red", "red", "orange", "red", "red"),
    type = "warning")

e <- simpleError(my_msg)
tryCatch(log("foo"), error = function(e) message(my_msg))
```


